### 2016-05-04 ch03-lrm/nonparametric.tex
Improve structure in CH03, add workflow figure
Add thumb index
Some cleanup here and there

\chapter{Non-parametric Modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}
\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.
}{Douglas Adams}{}

@@

The \gls{LPM} can be understood as a specific case of the \gls{LRM}: for  $\order{A} = 0$, the \gls{LRM} reduces to the \gls{LPM}.
As such, we use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, \order{B}, 0, \order{C}}$.
In the remainder of this text, we refer to \gls{LRM} as a group of methods which have $\order{A} \neq 0$ to make the distinction with \gls{LPM} more obvious.

@@

\begin{remark}
The methods proposed by \citet{Stenman2001ASFRF,Stenman2000ASETFE} also refer to `local polynomial regression' to smoothen the \gls{FRF}.
It should be noted, however, that such methods differ significantly from the \gls{LPM}.
Specifically, those methods operate directly on the raw \gls{ETFE}, in contrast to the \gls{LPM} which uses the input-output spectra and can hence estimate both an \gls{FRF} and a transient contribution.
Moreover, the methods proposed by \citet{Stenman2001ASFRF} build upon `local regression` approaches such as \gls{LOWESS}.
See e.g. \citet{Loader1999} for more information regarding these `local regression' approaches.
\end{remark}

@@

\section{LPM with impulse response truncation}
\input{\thisDir/truncation.tex}

>>>>

\chapter{Non-parametric Modeling}
\AddThumb{Non-parametric Modeling}
\label{sec:nonparametric}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}

@@

The \gls{LPM} can be understood as a specific case of the \gls{LRM}: for  $\order{A} = 0$, the \gls{LRM} reduces to the \gls{LPM}.
As such, we use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, \order{B}, 0, \order{C}}$.
In the remainder of this text, we refer to \gls{LRM} as a group of methods which have $\order{A} \neq 0$ to make the distinction with \gls{LPM} more obvious.
For more information regarding \gls{LPM}, we refer to e.g. \citet{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,Gevers2011lpm}.

@@

\begin{remark}
The methods proposed by \citet{Stenman2001ASFRF,Stenman2000ASETFE} also refer to `local polynomial regression' to smoothen the \gls{FRF}.
It should be noted, however, that such methods differ in a few aspects from the \gls{LPM}.
Specifically, those methods operate directly on the raw \gls{ETFE}, in contrast to the \gls{LPM} which uses the input-output spectra and can hence estimate both an \gls{FRF} and a transient contribution.
Moreover, the methods proposed by \citet{Stenman2001ASFRF} build upon `local regression` approaches such as \gls{LOWESS}.
See e.g. \citet{Loader1999} for more information regarding these `local regression' approaches.
\end{remark}

@@

\section{Smoothing the \glsentryshort{FRF} by Impulse Response Truncation}
\input{\thisDir/truncation.tex}
